The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-08-10 manuscript.Rmd
[fix #48] compare prop. of global diversity represented by phyla

Further biases exist across phyla and body size. Large-bodied and easily acccessible (e.g. dried specimens like shells, corals, echinoderms) are overrepresented in museum collections, compared with small less accessible organisms, such as the meiofauna. Of `r n_idigbio_phyla` phyla represented in iDigBio, `r records_rare_phyla$n_rare_phyla` have <500 records, and make up `r records_rare_phyla$prop_rare_phyla`% of the records. Yet, these undersampled taxa, especially those of small body size, are often the most abundant, and are likely to play an important role in the detection of changes in environmental quality[@Bik2012]. Additionally, the ecological implications of changes in the structure and composition of the communities of these small-bodied organisms, on higher trophic levels and ecosystems are largely unexplored.

>>>>

Further biases exist across phyla and body size. Large-bodied and easily acccessible (e.g. dried specimens like shells, corals, echinoderms) are overrepresented in museum collections, compared with small less accessible organisms, such as the meiofauna. Of `r n_idigbio_phyla` phyla represented in iDigBio, `r records_rare_phyla$n_rare_phyla` have <500 records, and make up `r records_rare_phyla$prop_recs_rare_phyla`% of the iDigBio records. This underrepresentation is manifested at the species level, while `r records_rare_phyla$prop_spp_rare_phyla_collected`% (n = `r format(records_rare_phyla$total_spp_rare_phyla_collected, big.mark=",")` total species) of the global number of species for the `r records_rare_phyla$n_rare_phyla` phyla occur in iDigBio, this proportion rises to `r records_rare_phyla$prop_spp_common_phyla_collected`% (n = `r format(records_rare_phyla$total_spp_common_phyla_collected, big.mark=",")`). Yet, these undersampled taxa, especially those of small body size, are often the most abundant, and are likely to play an important role in the detection of changes in environmental quality[@Bik2012]. Additionally, the ecological implications of changes in the structure and composition of the communities of these small-bodied organisms, on higher trophic levels and ecosystems are largely unexplored.
